Publications

### 2025-08-19 papers.qmd
minor edit text (250819GH)

These publications were written as part of STRATOS-TG2. Their aim is guidance on the topic of variable and functional form selection.

@@

Here we list a number of textbooks and papers that were written outside of STRATOS-TG2 by TG2 members or other authors. These materials are endorsed here because they fit the aim of guidance on selection of variables and functional forms in multivariable modeling.

>>>>

These publications were written on behalf of STRATOS-TG2. They center around the topic group's core topic, the selection of variables and functional forms in multivariable models.

@@

Here we list a number of textbooks and papers that were not written on behalf of STRATOS-TG2. These materials are endorsed here because they fit the aim of guidance on selection of variables and functional forms in multivariable modeling.
